---
title: "2021 PA Redistricting Maps"
author: "Geoffrey Arnold"
date: "12/17/2021"
output:
  html_document:
    toc: true
    theme: flatly
    toc_depth: 2
---

<!-- Wider contents --> 
<style type="text/css">
.main-container {
  max-width: 1250px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width="100%")

require(sf)
require(leaflet)

house <- read_sf("https://www.redistricting.state.pa.us/Resources/GISData/Districts/Legislative/House/2021-Preliminary/JSON/LRC-H-Preliminary.json")

house_labs <- house %>% st_transform() %>% st_centroid()

house_curr <- read_sf("https://data.pa.gov/api/geospatial/in5u-czi3?method=export&format=GeoJSON")

house_curr_labs <- house_curr %>% st_transform() %>% st_centroid()

senate <- read_sf("https://www.redistricting.state.pa.us/Resources/GISData/Districts/Legislative/Senate/2021-Preliminary/JSON/LRC-S-Preliminary.json")

senate_labs <- senate %>% st_transform() %>% st_centroid()

senate_curr <- read_sf("https://data.pa.gov/api/geospatial/vdjs-93zj?method=export&format=GeoJSON")

senate_curr_labs <- senate_curr %>% st_transform() %>% st_centroid()

pal <- colorFactor(palette = c("blue", "orange"), domain = c("Current", "2021 Proposal"))
```

# Purpose

I was very tired of staring at PDF's and screenshots so I made these to help with comparing the 2011 and preliminary PA Congressional and Senate Districts.

[GitHub Rep](https://github.com/geoffreylarnold/redisistricting_maps)

## Instructions

Leaflet will place whichever layer you most recently added to a Map on-top. For example: If you would like the "Current" House Districts to appear on-top, simply un-check the layer from the box on the top right and then select it again.

# House Preliminary Map

```{r house}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = house_curr,
              color = "blue",
              group = "Current") %>%
  addLabelOnlyMarkers(data = house_curr_labs,
                   label = ~leg_distri,
                   labelOptions = labelOptions(noHide = T, 
                                               textOnly = TRUE, 
                                               style = list("color" = "blue",
                                                            "font-size" = "12px")),
              group = "Current") %>%
  addPolygons(data = house,
              color = "orange",
              group = "2021 Proposal") %>%
  addLabelOnlyMarkers(data = house_labs,
                   label = ~District,
                   labelOptions = labelOptions(noHide = T, 
                                               textOnly = TRUE, 
                                               style = list("color" = "orange",
                                                            "font-size" = "12px")),
              group = "2021 Proposal") %>%
  addLayersControl(overlayGroups = c("2021 Proposal", "Current"),
                  options = layersControlOptions(collapsed = FALSE)) %>%
  addLegend(title = "Layers",
            pal = pal,
            values = c("Current", "2021 Proposal"),
            position = "bottomright")
```

# Senate Preliminary Map

```{r senate}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = senate_curr,
              color = "blue",
              group = "Current") %>%
  addLabelOnlyMarkers(data = senate_curr_labs,
                   label = ~name,
                   labelOptions = labelOptions(noHide = T, 
                                               textOnly = TRUE, 
                                               style = list("color" = "blue",
                                                            "font-size" = "12px")),
              group = "Current") %>%
  addPolygons(data = senate,
              color = "orange",
              group = "2021 Proposal") %>%
  addLabelOnlyMarkers(data = senate_labs,
                   label = ~District,
                   labelOptions = labelOptions(noHide = T, 
                                               textOnly = TRUE, 
                                               style = list("color" = "orange",
                                                            "font-size" = "12px")),
              group = "2021 Proposal") %>%
  addLayersControl(overlayGroups = c("2021 Proposal", "Current"),
                  options = layersControlOptions(collapsed = FALSE)) %>%
  addLegend(title = "Layers",
            pal = pal,
            values = c("Current", "2021 Proposal"),
            position = "bottomright")
```
